Safe Shared Memory for Concurrent Algol

### 2017-10-12 proposal.tex
more citation

@@

\section{Background on programming langauges}

@@

Of course, this was a very trivial example, but this methodology
scales up to problems of seemingly arbitrary complexity. For instance,
a type system inspired by Kripke semantics and the modal logic S5 has
been deployed in the ML5 language for distributed computing, enabling
one to develop distributed applications within a single unified
program~\cite{murphy-crary-harper:2008}. Concurrency primitives have
been added to functional languages such as
Facile~\cite{giacolone:1989}, Concurrent ML~\cite{reppy:1991,reppy:2007},
JOCaml~\cite{conchon-fessant:1999}, Concurrent
Haskell~\cite{jones-gordon-finne:1996} and Concurrent
Algol~\cite{harper:2016}. In another work, Balzer and Pfenning
augmented the session-typed linear logic with shared memory, using
shared channels and shared memory with an acquire-release discipline.

>>>>

\usepackage{sectsty}
\allsectionsfont{\sffamily}

@@

\section{What are languages good for?}

@@

Of course, this was a very trivial example, but this methodology
scales up to problems of seemingly arbitrary complexity. For instance,
a type system inspired by Kripke semantics and the modal logic S5 has
been deployed in the ML5 language for distributed computing, enabling
one to develop distributed applications within a single unified
program~\cite{murphy-crary-harper:2008}. Concurrency primitives have
been added to functional languages such as
Facile~\cite{giacolone:1989}, Concurrent
ML~\cite{reppy:1991,reppy:2007}, JOCaml~\cite{conchon-fessant:1999},
Concurrent Haskell~\cite{jones-gordon-finne:1996},
Rust~\cite{turon:2012}, Go~\cite{donovan:2015} and Concurrent
Algol~\cite{harper:2016}. In another work, Balzer and Pfenning
augmented the session-typed linear logic with shared memory, using
shared channels and shared memory with an acquire-release discipline.
